Performance of two different ontological and data access methods

### 2014-07-02 cold2014/magnus.tex
introducing the ontologies
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@707 43ef1190-90fd-4dd7-a769-d0121f02b80e

We present two different approaches, one promoted by Renault, see
\cite{SemWebAppRes} and \cite{ren1}, and another made by Martin~Hepp
in collaboration with Volkswagen resulting in amongst other things,
the Car Options Ontology~\cite{COO}. We shall compare them to find
their strengths and weaknesses. Each approach contains an ontology and
has its own way of representing data.  To make this comparison we have
used data about the same domain, data about car models and their
component constraints.  The first approach is a generic ontology. By
generic it means that it can be used to represent any product model
with component constraints. The second approach is a domain specific
ontology which as the name implies, is only applicable with one
particular domain. In this thesis that domain is about car models.

@@

We set out to evaluate different approaches based on a real use case
where a user is seeking to buy a new car based on detailed data
published by car manufacturers. Today only Renault, of all the car
manufacturers, has opened their data using semantic
technologies. Volkswagen had their data published until the start of
2013, but unfortunately they canceled their Semantic Web project and
the data were removed.  Fortunately, their ontologies are still open
for the community to use. Eventually, we found Daimler very
forthcoming, as they offered data about their A- and B-class cars.
The Daimler data used a custom XML-based format, so we lifted the data
using a Python script into the ontologies developed by Martin Hepp and
Volkswagen.

>>>>

We present two different approaches. One is promoted by Renault, see
\cite{SemWebAppRes} and \cite{ren1}. They have developed the
Configuration Ontology (CO) \cite{confOnt}, and developed an API to allow
users to traverse the RDF graph to find a smaller result set of cars.
The ontology focuses on building an RDF graph to represent all valid
configurations for a product model with component constraints.  It is
also made so that it is not needed to do any reasoning to get a valid
result set.  They call it a traversal of \textit{Configurations} which
will end up with a \textit{Partially Defined Products}
(PDP)\footnote{Partially Defined Product is a way of defining a
  product without using all of the features. For instance a car which
  may have many features, but we describe it as a car with mp3 and
  sunroof.}.  Their method insists there is a starting point, which is
a car model. From there, there is a \emph{lexicon} which can be used
to choose different specifications which may lead to a valid
configuration. There are also stated if some specifications are
impossible in the current configuration.  These are represented by
either the \textit{co:possible} or \textit{co:impossible}
property. Furthermore, string comparison must be used to check if a
certain specification is representing for instance fuel type.

The other approach was made by Martin~Hepp in collaboration with
Volkswagen resulting in the Car Options Ontology (COO) \cite{COO} and
the Vehicle Sales Ontology (VSO). They are designed to be used in
combination with GoodRelations, also designed by Hepp. When using COO,
one defines a base car model, and a \emph{trim} is defined on the
base, while a derivative car model should specify compatibilities and
constraints between configurations, e.g. an electrical car does not
have a conventional gear box.

We shall compare them to find their strengths and
weaknesses. Each approach contains an ontology and has its own way of
representing data.  To make this comparison we have used data about
the same domain, data about car models and their component
constraints.  The first approach is a generic ontology. By generic it
means that it can be used to represent any product model with
component constraints. The second approach is a domain specific
ontology which as the name implies, is only applicable with one
particular domain. In this thesis that domain is about car models.

@@

We set out to evaluate different approaches based on a real use case
where a user is seeking to buy a new car based on detailed data
published by car manufacturers. Note that the implementation is not
itself an important contribution, it is the evaluation that is the key
contribution. Today only Renault, of all the car manufacturers, has
opened their data using semantic technologies. Volkswagen had their
data published until the start of 2013, but unfortunately they
canceled their Semantic Web project and the data were removed.
Fortunately, their ontologies are still open for the community to
use. Eventually, we found Daimler very forthcoming, as they offered
data about their A- and B-class cars.  The Daimler data used a custom
XML-based format, so we lifted the data using a Python script into the
ontologies developed by Martin Hepp and Volkswagen.
